The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-09-13 paper.tex
Added Chaha summary

\section{CCCC clusters}

@@

\subsection{Predictions of CCC rankings}

@@

\section{Summary: Chaha}

@@

In the final tally, therefore, % TODO

>>>>

\subsection{CCCC clusters}

@@

\subsubsection{Predictions of CCC rankings}

@@

\subsection{Summary: Chaha}

@@

In the final tally, the {\sc Sonority Angle}-based approach fares worse on one datapoint and uses approximately the same number of constraints, but manages to accomplish most of the work of the analysis with the only crucial ranking being the placement of a single {\sc Ident(SonAngle)}$<$n constraint with respect to a relevant $\mathcal{M}$ constraint, while in Rose's analysis this work is spread over a number of different sonority-related constraints.
